\sys: Automated Data-Parallel Shell Processing

### 2020-04-12 pldi/microbenchmarks-table.tex
Update the formating of the microbenchmarks table

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllll}
\toprule
Script ~&~ Structure & Input &Seq Time & Script Size(\todo{20, 100}) &Compile Time (\todo{20, 100}) & Highlights \\
\midrule
\tti{grep} ~&~ $3\times$\tsta & 1~GB & 4809.61~s & \todo{\#Commands} & 63.37~ms\qquad 965.72~ms & complex NFA regex \\
\tti{sort} ~&~ $\tsta, \tpur$ & 10~GB & 1429.04~s & \todo{\#Commands} & 201.12~ms\qquad 2005.70~ms & \tti{sort}ing \\
\tti{top-n} ~&~ $2\times\tsta, 4\times\tpur$ & 10~GB & 4373.79~s & \todo{\#Commands} & 169.50~ms\qquad 3340.67~ms & double \tti{sort}, \tti{uniq} reduction \\
\tti{wf} ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 1351.91~s & \todo{\#Commands} & 165.41~ms\qquad 3325.32~ms & double \tti{sort}, \tti{uniq} reduction \\
\tti{grep-light} ~&~ $3\times$\tsta & 100~GB & 98.21~s & \todo{\#Commands} & 35.33~ms\qquad 355.90~ms & $3\times$\tsta \\
\tti{spell} ~&~ $4\times\tsta, 3\times\tpur$ & 1~GB & 481.13~s & \todo{\#Commands} & 311.45~ms\qquad 6655.26~ms & comparisons (\tti{comm}) \\
\tti{shortest-scripts} ~&~ $5\times\tsta, 2\times\tpur$ & \todo{UNKNOWN} & 1706.75~s & \todo{\#Commands} & 305.33~ms\qquad 6729.06~ms & \todo{extensive file-system operation} \\
\tti{diff} ~&~ \todo{TODO} & 10~GB & 1610.09~s & \todo{\#Commands} & 312.08~ms\qquad 4569.23~ms & non-parallelizable \tti{diff}ing \\
\bottomrule
\end{tabular*}

>>>>

\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lllllll}
\toprule
Script ~&~ Structure & Input &Seq Time & Script Size(\todo{20, 100}) &Compile Time (\todo{20, 100}) & Highlights \\
\midrule
\tti{grep} ~&~ $3\times$\tsta & 1~GB & 80m9.607s & \todo{\#Commands} & 0.063s\qquad 0.966s & complex NFA regex \\
\tti{sort} ~&~ $\tsta, \tpur$ & 10~GB & 23m49.044s & \todo{\#Commands} & 0.201s\qquad 2.006s & \tti{sort}ing \\
\tti{top-n} ~&~ $2\times\tsta, 4\times\tpur$ & 10~GB & 72m53.786s & \todo{\#Commands} & 0.170s\qquad 3.341s & double \tti{sort}, \tti{uniq} reduction \\
\tti{wf} ~&~ $3\times\tsta, 3\times\tpur$ & 10~GB & 22m31.907s & \todo{\#Commands} & 0.165s\qquad 3.325s & double \tti{sort}, \tti{uniq} reduction \\
\tti{grep-light} ~&~ $3\times$\tsta & 100~GB & 1m38.212s & \todo{\#Commands} & 0.035s\qquad 0.356s & $3\times$\tsta \\
\tti{spell} ~&~ $4\times\tsta, 3\times\tpur$ & 1~GB & 8m1.131s & \todo{\#Commands} & 0.311s\qquad 6.655s & comparisons (\tti{comm}) \\
\tti{shortest-scripts} ~&~ $5\times\tsta, 2\times\tpur$ & \todo{UNKNOWN} & 28m26.746s & \todo{\#Commands} & 0.305s\qquad 6.729s & \todo{extensive file-system operation} \\
\tti{diff} ~&~ \todo{TODO} & 10~GB & 26m50.085s & \todo{\#Commands} & 0.312s\qquad 4.569s & non-parallelizable \tti{diff}ing \\
\tti{optimized bi-grams} ~&~ $3\times$\tsta, \tpur & 10~GB & 123m54.946s & \todo{\#Commands} & 0.136s\qquad 2.674s & optimized version of bigrams \\
\bottomrule
\end{tabular*}
